\documentclass[aps,twocolumn,nofootinbib]{revtex4-1}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{floatrow}
\usepackage{subcaption}
\usepackage{xcolor}


\begin{document}
\title{Integrated Computational Materials Engineering Investigation of Additively Manufactured Ti-5553 Octet Truss Lattice Unit Cells}
\author{Nathan S. Johnson}
\affiliation{Colorado School of Mines}
\affiliation{Los Alamos National Laboratory}

\author{Maria Strantza, Jenny Wang, Manyalibo Matthews}
\affiliation{Lawrence Livermore National Laboratory}

\author{Dave Macknelly}
\affiliation{Atomic Weapons Establishment}

\author{Jun-Sang Park, Peter Kenesei}
\affiliation{Argonne National Laboratory}

\author{Bj\o rn Clausen, Cheng Liu, Donald W. Brown, John S. Carpenter}
\affiliation{Los Alamos National Laboratory}

\author{Craig A. Brice, Aaron P. Stebner}
\affiliation{Colorado School of Mines}

\begin{abstract}
Additive manufacturing has made the fabrication of complex geometries with small feature sizes possible in recent years. One technology AM is uniquely suited to benefit are octet truss lattice structures. The octet truss lattice structure for structural applications was first described in the theory of Ashby, Deshpande, and Fleck in the late 1990s and has seen an increase in use recently. Among the many applications of octet trusses are for lightweighting structural applications in defense, aerospace, and biomedical applications. However, the impact of the additive manufacturing process has not yet been elucidated for these materials. Octet truss lattice structures were manufactured using selective laser melting in a 2x1x1 unit geometry and subjected to uniaxial compression. A suite of characterization techniques was used to study the samples during compression including high energy X-ray diffraction and digital image correlation. A second suite of characterization techniques was used to study the samples ex situ including X-ray computed tomography and texture mapping. All of this information was compared against a finite element model of the same geometry. It was discovered that anisotropy in distribution of mechanical strains existed due to residual stresses caused by the build process. Furthermore, the samples failed in a pure stretch mode as predicted by the DFA model. This result has implications for how the AM build process will impact mechanical properties of octet trusses manufactured on a larger scale.
\end{abstract}
\date{\today}
\maketitle

\input{Introduction}
\input{Characterization}
\input{Results}
\input{Discussion}
\input{Conclusions}

\bibliography{bib.bib}
\end{document}


