\subsection{Machine Learning Toolboxes}
Most of the machine learning algorithms and approaches discussed in this review are, in some form, free and openly accessible. Many machine learning packages exist across many different programming languages and platforms. Table \ref{data_tools} highlights a variety of computational tools and packages and their relevance to AM synthesis optimization. 

\begin{landscape}
           \renewcommand{\arraystretch}{0.8}
    \setlength{\tabcolsep}{5pt}
    \begin{center}

        \begin{longtable}{p{4cm}p{4cm}p{11cm}} 
                \endfirsthead
                \caption{Commonly-used machine learning, statistical analysis, and computer vision toolboxes. Some toolboxes listed are open source, while some are packaged with commercial software like MATLAB. \label{data_tools}} \\ \hline
           
            Language/Platform & Package & Applications  \\ 
           % \endhead


            \hline
            Python & scikit-learn \cite{sklearn} & General data mining toolbox; packages for classification, regression, clustering, dimensionality reduction, model selection, and data pre-processing. \newline \\
            		& tensorflow \cite{tensorflow} & Machine learning toolkit for data mining and data flows; specifically focuses on the use of neural networks and deep learning for model building and problem solving. \newline \\
			& keras \cite{keras} & Deep learning-specific machine learning toolbox; designed for intuitive building of neural network systems. \newline \\
			& OpenCV \cite{opencv} & Algorithm toolbox for machine learning and computer vision; contains wide range of tools for image processing including image pre-processing, template matching, object identification, and convolutional neural networks. \newline \\
			
	   MATLAB & Statistics and Machine Learning Toolbox \cite{matlabml} & Commercial data analysis and machine learning toolbox with a wide range of applications in data analysis including clustering, classification, regression, and dimensionality reduction. \newline \\
	   		&\raggedright Computer Vision Toolbox\cite{matlabcv} & Algorithm toolbox for machine learning and computer vision; contains tools for a wide range of image analysis including pre-processing, object identification, template matching, and convolutional neural networks. \newline \\ 
			
	  C $++$ & OpenCV \cite{opencv} & Algorithm toolbox for machine learning and computer vision; contains wide range of tools for image processing including image pre-processing, object identification, template matching, and convolutional neural networks. \newline \\
	  	& tensorflow \cite{tensorflow} & Machine learning toolkit for data mining and data flows; specifically focuses on the use of neural networks and deep learning for model building and problem solving. \newline \\ 
		
	R & Machine Learning in R (MLR) \cite{mlr} & Infrastructure for incorporating common machine learning functions in R in an easy way; provides robust packages for a wide range of machine learning-based tools including regression, classification, clustering, sampling methods, model optimization and more; has built in parallelization methods. \newline \\  \hline
	
            \bottomrule
        \end{longtable}

    \end{center}
    
\end{landscape}

