\subsection{The Design Space of Additive Manufacturing}
The \textbf{design space} of additive manufacturing is the set of all machine parameters and measurable manufacturing phenomenon or material properties that result from the manufacturing process. It is summarized in Figure \ref{AMgene}. An example of controllable machine parameters can be found in Table \ref{table:design_space}. Measurable manufacturing phenomenon are quantities indicative of the processing history of the part. Examples include melt pool morphology, temperature, cooling rates, reflected intensity, and more. Measurable material properties are just that -- aspects of the final part which are relevant to scientific or engineering applications. 

The term `design space' will be used throughout this article to discuss the set of all additive manufacturing data which can be used with data-driven methods and machine learning algorithms. A single set of machine parameters, observed process phenomenon, and measured material properties can be considered as a \textit{coordinate} in the design space. As an example, consider a list of parameters for a laser powder bed fusion process, such as: Alloy Composition, Laser Power, Scan Speed, Maximum Melt Pool Temperature, Average Cooling Rate, Final Density, Young's Modulus, Ultimate Tensile Strength. Any part which is manufactured under a single set of conditions and is observed to have a set thermal history and material properties can be considered to be manufactured \textit{at that point} in the design space.

Representing data in the design space properly will be a major pre-processing step for machine algorithms to be amenable to AM optimization.

\begin{table*}[t]
    \renewcommand{\arraystretch}{0.8}
    \setlength{\tabcolsep}{5pt}
    \begin{center}
        \begin{tabular}{@{}llll@{}}
            \toprule
            \hline
             Parameter & range & step size & levels \\ \midrule
            \hline
            \hline
            Skin/Contour/Core laser parameters: & & & \\
            Power & 100-200 W & 10 W & 10 \\
            Scan speed & 500-1000 mm/s & 100 mm/s & 5 \\
            Spot size & 50-100 $\mu$m & 10 $\mu$m & 5 \\
            Energy density & 1-5 J/mm$^2$ & 1 J/mm$^2$ & 5 \\
            \hline
            Build parameters: & & & \\
            Polar angle & 0-90$^\circ$ & 30$^\circ$  & 4 \\
            Azimuth angle & 0-180$^\circ$ & 90$^\circ$  & 3 \\
            Sieve count & 0-10 & 2 & 5 \\
            Amount of recycled powder & 0-100\% & 10\% & 10 \\
            \hline
            Other parameters: & & & \\
            Blade direction & 0-300 mm & 10 mm  & 30 \\
            Transverse direction & 0-300 mm & 10 mm  & 30 \\
            Hatch spacing & 0.1-0.50 mm & 0.1 nm  & 5 \\
            \hline
            \bottomrule
        \end{tabular}
        \caption{A possible design space for laser powder bed fusion additive manufacturing. There are over $10^9$ possible combinations of machine inputs, based on the listed ranges and step sizes. Any possible combination of these parameters is a point in the design space.}
        \label{table:design_space}
    \end{center}
\end{table*}
